### 2024-10-10 Article/main.tex
lemma 2.2.3

@@

Regular monos in $\mathbf{EqGrph}$ are then natural transformations $\eta: \eqgraph{G \dot\rightarrow H}$ such that $\eta_Q$ is mono (\Cref{prop:reg_mono_in_EG_are_mono_in_graph}). Since limits are computed pointwise, pullbacks preserve regular monomorphisms (\Cref{prop:monos_pres_by_pullback}). Regular monos are preserved also by pushouts. Again, since (co)limits are computed pointwise, and in $\Set$ monos are preserved by pushouts (since $\Set$ is adhesive), we can conclude what follows.

@@

>>>>

Here it follows an interesting property of adhesive categories~\cite{lack2011embeddingtheoremadhesivecategories}.

\begin{prop}\label{prop:monos_are_preserved_by_pullbacks_in_adh_cats}
    In any adhesive category, the pushout of a monomorphism along any morphism is a monomorphism, and the resulting square is also a pullback.
\end{prop}

@@

\color{red}{

\begin{lemma}\label{lemma:reg_mono_pres_by_pushouts}
    Pushouts in $\mathbf{EqGrph}$ preserves regular monomorphisms.    
\end{lemma}

\begin{proof}
    Consider the following pullback in $\mathbf{EqGrph}$, where $m$ is a regular monomorphism:
    \[
        \begin{tikzcd}
            G \arrow[r, "m"] \arrow[d, "n" swap] & G_1 \arrow[d, "i"] \\
            G_2 \arrow[r, "j" swap] & P
        \end{tikzcd}
    \]
    In particular, since $\mathbf{EqGrph}$ is a category of presheaves, colimits are computed pointwise,\color{green}{commentato}\color{black}

    %%% IDEA: far vedere che, poiché i colimiti in una categoria di prefasci sono calcolati punto punto, allora ho un pushout su ogni componente (E, V, Q). Dalla prop nella parte sull'adesività si può concludere che tutti e tre i pushout preservano mono e quindi mono è preservata su tutte e tre le componenti, quindi reg  mono.
\end{proof}

}\color{black}
Regular monos in $\mathbf{EqGrph}$ are then natural transformations $\eta: \eqgraph{G \dot\rightarrow H}$ such that $\eta_Q$ is mono (\Cref{prop:reg_mono_in_EG_are_mono_in_graph}). Pullbacks preserve regular monomorphisms (\Cref{prop:monos_pres_by_pullback}). Regular monos are preserved also by pushouts (\Cref{lemma:reg_mono_pres_by_pushouts}). Again, since (co)limits are computed pointwise, and in $\Set$ monos are preserved by pushouts (since $\Set$ is adhesive), we can conclude what follows.

@@

% Q crea pullback, Q crea pushout sui reg mono.
